---
title: "5243_Project1"
author: "Yufei Wang"
date: "2023-09-13"
---


```{r setup, include = FALSE, echo = FALSE}

library(tidyverse)
library(tidytext)
library(tm)
library(RColorBrewer)
library(plotly)
library(wordcloud)
library(ggplot2)
library(shiny) 
library(dplyr)
library(DT)
library(scales)
library(gridExtra)
library(ngram)
library(rsconnect)

```

```{r}
urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/cleaned_hm.csv'
hm_data <- read_csv(urlfile)

urlfile<-'https://raw.githubusercontent.com/rit-public/HappyDB/master/happydb/data/demographic.csv'
demographic_data <- read_csv(urlfile)

```
```{r text processing in tm,warning=FALSE, message=FALSE,echo=FALSE}
corpus <- VCorpus(VectorSource(hm_data$cleaned_hm))%>%
  tm_map(content_transformer(tolower))%>%
  tm_map(removePunctuation)%>%
  tm_map(removeNumbers)%>%
  tm_map(removeWords, character(0))%>%
  tm_map(stripWhitespace)
```

#Clean the data

Firstly I cleaned the raw data and combined it with demographic data.

```{r stemming,warning=FALSE, message=FALSE,echo=FALSE}
stemmed <- tm_map(corpus, stemDocument) %>%
  tidy() %>%
  select(text)
```


```{r tidy dictionary,warning=FALSE, message=FALSE,echo=FALSE}
dict <- tidy(corpus) %>%
  select(text) %>%
  unnest_tokens(dictionary, text)
```

```{r stopwords,warning=FALSE, message=FALSE,echo=FALSE}
data("stop_words")

word <- c("happy","lot","today","months","month",
                 "happier","happiest","last","week","past","day","time", "ago","yesterday", "feel")

stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
```

```{r tidy stems with dictionary,warning=FALSE, message=FALSE,echo=FALSE}
completed <- stemmed %>%
  mutate(id = row_number()) %>%
  unnest_tokens(stems, text) %>%
  bind_cols(dict) %>%
  anti_join(stop_words, by = c("dictionary" = "word"))
```

```{r stem completion, warning=FALSE, message=FALSE,echo=FALSE}
completed <- completed %>%
  group_by(stems) %>%
  count(dictionary) %>%
  mutate(word = dictionary[which.max(n)]) %>%
  ungroup() %>%
  select(stems, word) %>%
  distinct() %>%
  right_join(completed) %>%
  select(-stems)
```

```{r reverse unnest,warning=FALSE, message=FALSE,echo=FALSE}
completed <- completed %>%
  group_by(id) %>%
  summarise(text = str_c(word, collapse = " ")) %>%
  ungroup()
```

```{r cleaned hm_data, warning=FALSE, message=FALSE,echo=FALSE}
hm_data <- hm_data %>%
  mutate(id = row_number()) %>%
  inner_join(completed)
```

```{r}
hm_data <- hm_data %>%
  inner_join(demographic_data, by = "wid") %>%
  select(wid,
         gender, 
         marital, 
         parenthood,
         reflection_period,
         age, 
         country, 
         original_hm,
         ground_truth_category, 
         predicted_category,
         text) %>%
  mutate(count = sapply(hm_data$text, wordcount)) %>%
  filter(marital %in% c("single", "married","divorced","separated","widowed")) %>%
  filter(gender %in% c("m", "f")) %>%
  filter(parenthood %in% c("n", "y")) %>%
  filter(reflection_period %in% c("24h", "3m")) %>%
  mutate(reflection_period = fct_recode(reflection_period, 
                                        months_of_3 = "3m", hours_of_24 = "24h"))
head(hm_data)
```

#Grouping by continent

From the data frame, we can see that there are many topics that we can choose to analyze, such as people's gender, martial region, etc. I decided to analyze people's happy moment by region. Firstly I'm going to demonstrate all of the countries in the table, and categorize them into different continent.


```{r}
table(hm_data$country)
`````

```{r}
data_asia <- hm_data[hm_data$country %in% c("AFG", "ARE", "ARM", "BGD", "BHR", "HKG", "IDN", "IND", "IRQ", "ISR", "JPN", "KAZ", "KOR", "KWT", "LKA", "MYS", "NPL", "PAK", "SAU", "SGP", "THA", "TWN", "UMI", "VNM"),]

data_europe <- hm_data[hm_data$country %in% c("ALB", "AUT", "BGR", "CYP", "CZE", "DEU", "DNK", "EST", "ESP", "FIN", "FRA", "GBR", "GRC", "HRV", "ITA", "LTU", "LVA", "MDA", "MKD", "MLT", "NOR", "PRT", "ROU", "RUS", "SVN", "SWE", "UKR"),]

data_na <- hm_data[hm_data$country %in% c("CAN", "USA"),]

data_sa <- hm_data[hm_data$country %in% c("ARG", "BRA", "CHL", "COL", "PER", "PRI", "VEN", "SUR", "URY"),]

data_oceania <- hm_data[hm_data$country %in% c("ASM", "AUS", "FJI", "KIR", "MHL", "NCL", "NZL", "PNG", "SLB", "TON", "TUV", "VUT"),]

data_africa <- hm_data[hm_data$country %in% c("DZA", "ETH", "GHA", "GMB", "KEN", "MAR", "NGA", "ZAF", "ZMB"),]

data_caribbean <- hm_data[hm_data$country %in% c("BRB", "JAM", "KNA", "PRI", "TCA", "TTO"),]
```

We can create wordclouds for each of the continent respectively.

#Asia
```{r, warning=FALSE}
wordcloud(words = data_asia$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

#Europe
```{r, warning=FALSE}
wordcloud(words = data_europe$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

#North America
```{r, warning=FALSE}
wordcloud(words = data_na$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

#South America

```{r, warning=FALSE}
wordcloud(words = data_sa$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

#Oceania

```{r, warning=FALSE}
wordcloud(words = data_oceania$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

#Africa
```{r, warning=FALSE}
wordcloud(words = data_africa$text, min.freq = 1, max.words=40, 
          random.order=FALSE, rot.per=0.4, colors=brewer.pal(8, "Dark2"))
```

From the above wordcloud, we can see that No matter what continent people are on, "friend" and "family" are the most important factors of people's happiness. However, there are also differences between people from different contingents. For instance, Asian tends to spend time enjoying movies, and gaining happiness from the movies and the moment, while European pays attention to whether they win something. Interestingly, for people living in Oceania, "life" is the most significant reason for their happiness.



```{r, warning=FALSE}
oceania_text <- data_oceania$text
all_words <- unlist(strsplit(oceania_text, " "))
word_freq <- table(all_words)
word_freq_df <- data.frame(word = names(word_freq), freq = as.numeric(word_freq))
word_freq_df <- word_freq_df[order(word_freq_df$freq, decreasing = TRUE), ]
top_10_words <- head(word_freq_df, 10)
print(top_10_words)
```

